Extracting production locations for each species to obtain environmental forcings

### 2025-07-10 02_extracting_production_locations.qmd
All species

quantity <- quantity %>% 
  mutate(
    environment = as.factor(environment),
    Scientific_Name = as.factor(Scientific_Name),
    status_nm = as.factor(status_nm),
    status_description = as.factor(status_description),
    country = as.factor(country),
    fao_fishing_area = as.factor(fao_fishing_area),
    ISO3_Code = as.factor(ISO3_Code)
  ) %>% 
  filter(
    Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae") &
    environment == "Marine" & 
    status_nm != "Not significant (<0.5)"
    )

>>>>

quantity <- quantity %>% 
  mutate(
    environment = as.factor(environment),
    Scientific_Name = as.factor(Scientific_Name),
    status_nm = as.factor(status_nm),
    status_description = as.factor(status_description),
    country = as.factor(country),
    fao_fishing_area = as.factor(fao_fishing_area),
    ISO3_Code = as.factor(ISO3_Code)
  ) %>% 
  filter(
    # Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae") &
    environment == "Marine" & 
    status_nm != "Not significant (<0.5)"
    )
